European or American? A re-examination of the transatlantic influence over the IMF

### 2025-05-21 manuscript/manuscript.qmd
fix citations after zotero key update

One renowned fact about the IMF and its sister institution, the World Bank, is the long-standing "gentlemen's agreement" of the IMF managing director being a European, and the World Bank president being an American [@Keating2024; @Weiss2023], despite no such provisions in either institution's articles of agreements [@Fund2020; @WorldBank2021].

@@

-   IMF chief European [@Kahler2001]

>>>>

One renowned fact about the IMF and its sister institution, the World Bank, is the long-standing "gentlemen's agreement" of the IMF managing director being a European, and the World Bank president being an American [@keating2024; @weiss2023], despite no such provisions in either institution's articles of agreements [@fund2020; @WorldBank2021].

@@

-   IMF chief European [@kahler2001]
